---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{D4CAE.dashboard}`

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of `{D4CAE.dashboard}` like so:

```{r}
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Run

You can prepare to run the app by running: 
```{r}
library("devtools")
library("golem")
golem::document_and_reload() 
source("./dev/01_start.R") 
run_app()  # ie D4CAE_dashboard::run_app()
```

You can launch the application by running:

```{r, eval = FALSE}
D4CAE.dashboard::run_app()
```

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("D4CAE.dashboard")
```

```{r, error = TRUE}
covr::package_coverage()
```

# Warnings
# package covr not installed 
